Verifying the \shaThree\ Implementation from \openssl\ with the Software Analysis Workbench

### 2022-05-12 paper/conclusion.tex
Add minor grammar and sentence structure changes

This paper presents the proof of the \shaThree\ implementation in \openssl\ using the \saw\ tool.
The proof is accomplished by writing a \cryptol\ specification for the \nist\ \fips\ publication that defines the \shaThree\ algorithm.
The \cryptol\ specification is aided with two additional \cryptol\ library functions, the for-method and while-method, to hide the functional list comprehensions.
The for-method being a parallel-for operating on each element in a list.
The while-method being iteration over a list.
The \cryptol\ is shown equivalent to the \fips\ standard though visual inspection and input to output matching on published test vectors.

>>>>

This paper presents the proof of the \shaThree\ implementation in \openssl\ using the \saw\ tool.
The proof is accomplished by writing a \cryptol\ specification for the \nist\ \fips\ publication that defines the \shaThree\ algorithm.
The \cryptol\ specification is aided with two additional \cryptol\ library functions, the for-method and while-method, to hide the functional list comprehensions.
The for-method is a parallel-for operating on each element in a list, and the while-method is a list iteration.
The \cryptol\ is shown equivalent to the \fips\ standard through visual inspection and input to output matching on published test vectors.

### 2022-05-12 paper/saw.tex
Add minor grammar and sentence structure changes

\saw\ supports hierarchical reasoning with \emph{overrides}.
An override replaces one \sawcore\ model with another in the formal analysis.
As an example, consider a C function \texttt{a}() that itself calls another C function as part of its implementation: \texttt{T a()} \{\texttt{... b() ...}\}.
The \sawcore\ from symbolic executions for \texttt{a()} of necessity inlines and executes the code for \texttt{b()}, and as a result, yields a model in \sawcore\ that is to big and complex to accomplish the equivalence proof between \texttt{a()} and the \cryptol\ specification of \texttt{a()}.
Now suppose that \texttt{b()} is specified in \cryptol.
If \saw\ is able to prove that the specification for \texttt{b()} and its C implementation are equivalent, then after symbolic execution an override is able to replace \texttt{b()} in \texttt{a()} with the \sawcore\ from the \cryptol\ for \texttt{b()}.

>>>>

\saw\ supports hierarchical reasoning with \emph{overrides}.
An override replaces one \sawcore\ model with another in the formal analysis.
As an example, consider a C function \texttt{a}() that itself calls another C function as part of its implementation: \texttt{T a()} \{\texttt{... b() ...}\}.
The \sawcore\ generated from symbolic executions for \texttt{a()} of necessity inlines and executes the code for \texttt{b()}, and as a result, yields a model in \sawcore\ that is too big and complex to accomplish the equivalence proof between \texttt{a()} and the \cryptol\ specification of \texttt{a()}.
Now suppose that \texttt{b()} is specified in \cryptol.
If \saw\ is able to prove that the specification for \texttt{b()} and its C implementation are equivalent, then after symbolic execution an override is able to replace \texttt{b()} in \texttt{a()} with the \sawcore\ from the \cryptol\ for \texttt{b()}.
